Developing a Bubble Chamber Particle Discriminator Using Semi-Supervised Learning

### 2019-03-01 documentation/report.tex
Renamed ICN

\begin{enumerate}
    \item Iterative Cluster Nucleation is inspired by unsupervised clustering algorithms, and takes advantage of the ``confidence'' of the neural network's predictions (that is, how close the predictions are to 0 or 1).

@@

    \item Gravitational Differentiation is an analog alternative to Iterative Cluster Nucleation. Using a novel piecewise exponential function for calculating final-layer derivatives, called $\mathrm{GravDiff}(p, \psi, g)$, unlabeled examples are caused to "gravitate" toward more accurate predictions based on the confidence of the neural network's predictions.

>>>>

\begin{enumerate}
    \item Iterative Clustering is inspired by unsupervised clustering algorithms, and takes advantage of the ``confidence'' of the neural network's predictions (that is, how close the predictions are to 0 or 1).

@@

    \item Gravitational Differentiation is an analog alternative to Iterative Clustering. Using a novel piecewise exponential function for calculating final-layer derivatives, called $\mathrm{GravDiff}(p, \psi, g)$, unlabeled examples are caused to "gravitate" toward more accurate predictions based on the confidence of the neural network's predictions.
